---
title: "inSilecoRef"
output:
  md_document
---

<!--

setwd('/users/davidbeauchesne/dropbox/phd/inSilecoRef/')
rmarkdown::render('./README.Rmd', 'md_document')

-->

```{r echo=FALSE}
knitr::opts_chunk$set(
  fig.path = "inst/assets/img/",
  comment = "R>> ",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 5,
  fig.height = 5
)
```

# Description

This package contains the tools used to manage bibliographic data for the
[*inSileco* blog](https://insileco.github.io/).

Managing bibliographies in a group can be hard considering that individuals
use different types of reference management tools such as
[Zotero](https://www.zotero.org/) and [Mendeley](https://www.mendeley.com/).
To simplify reference management on our blog and still allow blog members to
use their own preferred reference management tools, we decided to build a
centralized repo with a common `.bib` file and tools to update and validate
this file.

## Status

[![Build Status](https://travis-ci.org/inSileco/inSileco.github.io.svg?branch=dev)](https://travis-ci.org/inSileco/inSileco.github.io)


# Installation

The easiest way to install `inSilecoRef` is to use the
[*devtools*](http://cran.r-project.org/web/packages/devtools/index.html) package:

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("inSileco/inSilecoRef")
```

# Main features

The package offers two main functions. The main function, `newDOI()` uses
digital object identifier (DOI) and takes advantage of functionalities offered
by the [`rcrossref`](https://ropensci.org/tutorials/rcrossref_tutorial/) package.
The second function, `newManual()` allows the user to create a manual entry in
cases where DOIs are not available.

## `newDOI()`

```{r newDOI}
newDOI(DOI = c('10.1016/j.tree.2016.10.011','10.1890/130230','10.1515/9781400881376'))
```


### To do list

- \[ \] `insileco.bib` blog complete bibtex file
- \[ \] `manual.bib` manual entries bibtex file
- \[ \] `newDOI()` function to insert new DOI in `doi.RDS` and `insileco.bib`
- \[ \] `newManual()` function to crete new manual entry for `manual.bib`


### Material

http://www.pauloldham.net/creating-a-bibliography-with-rcrossref/
